Best Practices for Developing Monte Carlo Methodologies in Molecular Simulations [Article v\versionnumber]

### 2025-06-02 paper/paper.tex
first three review responses

In general, the Metropolis acceptance criterion is given by,
\begin{equation}
\pi_{o\rightarrow n}=\min(1, \chi),
\end{equation}
where $\chi$ is the Metropolis acceptance probability.
The reverse acceptance probability is $\pi_{n\rightarrow o}=\min(1, 1/\chi)$.
The ratio of $\pi$ is then simplified as,
\begin{equation}
\frac{\pi_{o\rightarrow n}}{\pi_{n\rightarrow o}}=\frac{\min(1, \chi)}{\min(1, 1/\chi)} = \chi,
\label{eq:pi}
\end{equation}
by considering each of the three possibilities, $\chi < 1$, $\chi > 1$ and $\chi=1$, separately.
While the Metropolis acceptance criterion is used throughout this article, other alternatives are possible while maintaining detailed balance.

@@

An efficient implementation may have a displacement parameter, $\delta_i$, specifically tuned for each particle type, $i$.
This could be important to improve sampling in cases where the particle sizes or interactions are different.
In addition, particles are chosen from all mobile particles, $N_m$, for sampling efficiency.
A possibly inefficient alternative would be to define separate trials that select among specific particle types.
In that case, if there are more particles of one type than another, the species with fewer numbers would have a relatively larger probability of displacement.
%Although these trials could be assigned different weights to correct this relative probability, such weights would need to be recomputed when the number of particles changes.

@@

In the Gibbs ensemble, separate domains are simulated for which chemical and mechanical equilibrium at constant temperature is established between them \cite{panagiotopoulos_direct_1987}, although chemical equilibrium is sufficient to enforce mechanical equilibrium \cite{panagiotopoulos_adsorption_1987}.
For notational convenience, we will consider only two domains such that the total volume, $V=V_1+V_2$, is the sum of two volumes and the total number of particles of type $i$, $N_i$, is $N_{i1} + N_{i2}$.
Volume changes require scaling, as described in Section \ref{sec:rhs_npt}, and the particle positions must be expressed in terms of the scaled coordinates.
Although recent studies show that Gibbs (and all other) ensemble simulations may utilize a shell particle \cite{hatch_theory_2024}, we consider only the application of a shell particle in the $NPT$ ensemble in this article.

@@

If particle type $i$ and $j$ are identical, then $\delta_{ij}=1$.
Otherwise, $\delta_{ij}=0$.
Substituting Eq.~\ref{eq:rhs_muvt} into the first ratio in Eq.~\ref{eq:detailed_balance}, and using Table~\ref{tab:lhs_ins_avb} for the second ratio in Eq.~\ref{eq:detailed_balance}, results in
\begin{equation}
\chi = \frac{N_j}{N_j+\delta_{ij}}\left(\frac{v_{AV}z_i}{P_{\omega n}(N_i^{AV}+1)}\right) e^{-\beta\Delta U}.
\label{eq:lhs_gc_avb_add}
\end{equation}

>>>>

In general, the Metropolis acceptance criterion is given by,
\begin{equation}
\pi_{o\rightarrow n}=\min(1, \chi),
\end{equation}
where $\chi$ is the Metropolis acceptance probability.
The reverse acceptance probability is $\pi_{n\rightarrow o}=\min(1, 1/\chi)$.
The ratio of $\pi$ is then simplified as,
\begin{equation}
\frac{\pi_{o\rightarrow n}}{\pi_{n\rightarrow o}}=\frac{\min(1, \chi)}{\min(1, 1/\chi)} = \chi,
\label{eq:pi}
\end{equation}
by considering each of the three possibilities, $\chi < 1$, $\chi > 1$ and $\chi=1$, separately.
While the Metropolis acceptance criterion is used throughout this article, other alternatives are possible while maintaining detailed balance.\cite{barker_monte_1965}

@@

An efficient implementation may have a displacement parameter, $\delta_i$, specifically tuned for each particle type, $i$.
This could be important to improve sampling in cases where the particle sizes or interactions are different.
In addition, particles are chosen from all mobile particles, $N_m$.
A possible alternative would be to define separate trials that select among specific particle types.
In that case, if there are more particles of one type than another, the species with fewer numbers could have a relatively larger probability of displacement.
The relative efficiency of this alternative approach compared to the one derived here is beyond the scope of this article.
If the minor species is of more interest, the alternative could be more efficient.
On the other hand, inefficiencies could arise if the minor species were caged in solvent that was not as well sampled.
%Although these trials could be assigned different weights to correct this relative probability, such weights would need to be recomputed when the number of particles changes.

@@

In the Gibbs ensemble, separate domains are simulated for which chemical and mechanical equilibrium at constant temperature is established between them \cite{panagiotopoulos_direct_1987}, although chemical equilibrium is sufficient to enforce mechanical equilibrium \cite{panagiotopoulos_adsorption_1987}.
For notational convenience, we will consider only two domains such that the total volume, $V=V_1+V_2$, is the sum of two volumes and the total number of particles of type $i$, $N_i$, is $N_{i1} + N_{i2}$.
Volume changes require scaling, as described in Section \ref{sec:rhs_npt}, and the particle positions must be expressed in terms of the scaled coordinates.
We do not consider constant-pressure Gibbs ensemble in this work \cite{panagiotopoulos_phase_1988}.
Although recent studies show that Gibbs (and all other) ensemble simulations may utilize a shell particle \cite{hatch_theory_2024}, we consider only the application of a shell particle in the $NPT$ ensemble in this article.

@@

If particle type $i$ and $j$ are identical, then $\delta_{ij}=1$.
Otherwise, $\delta_{ij}=0$.
Substituting Eq.~\ref{eq:rhs_muvt} into the first ratio in Eq.~\ref{eq:detailed_balance}, and using Table~\ref{tab:lhs_ins_avb} for the second ratio in Eq.~\ref{eq:detailed_balance}, results in
\begin{equation}
\chi = \frac{N_j}{N_j+\delta_{ij}}\left[\frac{v_{AV}z_i}{P_{\omega n}(N_i^{AV}+1)}\right] e^{-\beta\Delta U}.
\label{eq:lhs_gc_avb_add}
\end{equation}
